Response to reviewers

### 2018-02-01 manuscripts/AmNat_response_to_rev.Rmd
response to reviewers

--- 
title: "Response to reviewers"
author:
  - "Milad Memarzadeh"
  - "Carl Boettiger"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
bibliography: citations.bib
---

ASSOCIATE EDITOR'S RECOMMENDATION

Dear Professor Bronstein; Prof Dwyer,

> My recommendation is that manuscript 57722 be declined without prejudice.   The authors use a state of the art computer algorithm known as ``POMDP'' to determine, on the fly, how fisheries should be managed, in terms of the total amount of stock that can be harvested, and the profit accruing from that harvest.   This is an important problem in ecology, and the authors approach appears to offer significant insight.  The reviewers nevertheless point out some important ways in which the text could be improved, and reviewer 1 in particular argues that the authors's approach may be significantly flawed.  These problems would therefore need to be addressed for a revision to be successful.

@@

Reviewer 1's primary objection essentially re-asserts the "paradox of measurement uncertainty" that previous literature has also asserted: that uncertainty should somehow make less cautious.  We appreciate the reviewer highlighting the importance of explaning this central issue properly, and our revisions should make it clear how this erroneous and potentially dangerous conclusion arises from simplifying assumptions.  Reviewer 2's primary objection is the missed opportunity of focusing too narrowly on fisheries.  We agree entirely with the reviewer that the fundamental issues here are germane to ecological management and not specific to fisheries, and have revised the presentation substantially to address this.  Both reviewers raised concerns about the clarity of the methods; so in addition to rewritten discussion of methods we now provide fully executable code to replicate the analysis shown here.  Lastly but most importantly, both reviewers raise the observation that few fisheries are actually managed using a strict constant escapement (CE) policy.  We have introduced more realistic management strategies based on regulating fishing mortality through maximum sustainable yield (MSY) and total allowable catch (TAC), as additional comparisions.  TAC illustrates a different, more heuristic approach to uncertainty than seen in the optimal control methods that provides some valuable additional insights into the challenge of accounting for measurement error. We think this results in a much more interesting mansucript which should be relevant to the broad audience of the American Naturalist.

@@

This is a paradoxical conclusion that defies the precautionary principle, and as such would have important ramifications in ecological management in many applications beyond fisheries.  Further, though the reviewer's analysis is not identical to either the approaches of @Clark1986 or @Sethi2005 (neither assume constant escapement and both find this paradoxical result in only some but not all cases), we believe our analysis provides both a refutation of this result and a clear intutition as to where this misleading conclusion has come from.

@@

Figure 4 offers a clear explanation for when it is optimal to increase harvest in response to increased uncertainty: the POMDP harvest only exceeds the CE harvest when the measured stock size is erroneously low.  That is, when the prior belief would have suggested the observation should be much higher, and therefore the measurement is most likely an error under-estimating the true stock size.  This logic is entirely intuitive and is bourne out in the resulting POMDP policies.

@@

The reviewer and editor have raised an important issue in the question of whether we permit the harvest quota to be set to a value higher than the stock.  There are two problems with this.  First, it's not clear how the reviewer implements this assumption in the face of measurement uncertainty: how can one be certain a quota is less than 90% of stock size X without knowing what X is?  One can obviously enforce this with respect to the measured stock size but not the true stock size.  More importantly, this assumption amounts to the assertion that it is mathematically impossible to overfish a stock to the point of collapse.  However low the stock size might get, local extinction is impossible.  In this world-view, there will always be some tiny fraction of ato-fishes from which the population can recover.  Assuming that local extinction is impossible will indeed bias any optimal decision model to be more agressive.  Obviously this also has impliciations for ecological models in general, conservation policy would look different if we assumed extinction was impossible. @Clark1986 already recognized that a very similar assumption in @Reed1979 derivation that stochastic models needed no additional caution ($S=D$) was likely due to the fact that accidentally extinction was impossible (see manuscript, line 150). We do not adopt this assumption.  Obviously real world populations cannot be indefinitely reduced by only a fractional percentage. In our simulations, though we consider a Ricker model, stock abundances are divided into 100 distinct bins, with the smallest bin corresponding to a stock size of zero. Thus it is possible for overharvesting or stochastic environment, or some combination of both, to lead a population to permanenently collapse once it has gotten small enough.

@@

The presentation of all of this material has been entirely re-written in what we hope you will find is a much more appropriate and accessible style.  To avoid needless formalism, we do not rehash the technical details of solving Partially Observed Markov Decision Processes but instead point to the extensive literature already existing on the subject.  Instead, we focus on describing the nature of the problem and how it differs from analyses such as the perfectly observed Markov Decision Process that provides the basis for the Constant Escapement strategy (@Reed1979) and from other Bayesian hierarchical modeling (e.g. partially observed Markov processes, pomp, or Hidden Markov Models, HMMs) which are not decisison processes at all, but rather a prerequiste part of choosing & paramaterizing a model, not using said model to make a decision.

> In spite of these negative comments, it seems like the overall approach has a great deal of potential, as Reviewer 2 argues, and if Reviewer 1's concerns prove to be minor, then I believe that a revised version would be a substantial contribution.  That said, the complexity of the technical issues is quite high, and so it may be simpler to submit the manuscript to a journal that specializes in mathematical biology or in fisheries management.

Greg Dwyer

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

Reviewer #1:

For complete review, see the attached PDF, which begins as follows:

> I attempted to evaluate the papers overall conclusions by a very simple simulation and these results
seem to challenge the papers conclusions.
I simulated a population with the model the authors describe with both observation and process error
lognormally distributed and using the authors parameters. For a range of escapement goals I calculated
the net present value of using that escapement goal, and compared the consequences when there was
no observation error to the case where the lognormal cv was 0.5 – that is very high observation error.
The one difference I made was I did not let the harvest exceed 90% of the total population size ... this
seems reasonable as I know of few fisheries where 90% of the population could be harvested in a single
year.

> The graph below shows a typical result. The thin line is with no observation error, the ticker line with the observation error. In every case the optimal escapement goal was lower when observation error was included.

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.  We believe the differences in our respective results can be explained by the differences in our methods as discussed in our reply to the Editor's discussion of this issue. In short, we believe the reviewer's seemingly counter-intuitive result that increased uncertainty should be met with an action (lowering escapement) that would increase the risk of stock collapse rather then the intuitive response to be cautious by reducing harvest, is simply an artefact of the reviewer's assumption that stock collapse is impossible, and thus increased harvesting poses no real risk.

@@

We agree that the results and methodoloy could have been much more clearly presented. We hope the rewritten presentation of these results clarifies these issues. In particular, note that once you introduce measurement error a fixed escapement policy can only achieve a fixed *expected* escapement, you never know what the actual escapement is because you never know exactly how many fish you started with.  As measurement errors are equally likely to be too high or too low, a run of "heads", so to speak, would result in consistently overharvesting and continued decline (see discussion around line 363.)

@@

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

Reviewer #2:

@@

We thank the reviewer for this careful and constructive review, and agree entirely with the recommendation that the fundamental issues here are not limited to the problem of fishing quotas butare germane to much of ecological decision making. We have now tried both to set up the generic nature of the issue of measurement uncertainty (see Introduction) and discuss its implications beyond fisheries much more explicitly (e.g. lines 423 - 437).  We have however removed the treatment of the tipping point model in order to focus explicitly on the role of uncertainty in the more familiar case of logistic growth, where the dramatic consequences of measurement uncertainty may be less inutitive and cannot be dismissed merely by questioning the frequency of tipping points occurring in real systems.  We hope to address the problem of tipping points more explicitly and more fully in later work.

@@

We now include a formal comparison against TAC-based management policy (and also MSY based policy in the supplement), which reflect this aspect of today's actual management polcies which are not updated annually but apply a constant fishing effort (mortality). We also discuss several of the practical objections to implementing POMDP in practice and how it might be modified to address more of these concerns, e.g. lines 456-490.

@@

Excellent observation! Yes, due to the influence of the prior belief, POMDP is slightly more catious when a stock is rebuilding from small sizes

>>>>

--- 
title: "Response to reviewers"
author:
  - "Milad Memarzadeh"
  - "Carl Boettiger"
output: 
  pdf_document:
    fig_caption: true

bibliography: citations.bib
header-includes: |
  \usepackage{times}
  \usepackage{etoolbox}
  \usepackage[dvipsnames]{xcolor}
  \usepackage[framemethod=tikz]{mdframed}
  \let\oldquote\quote
  \let\endoldquote\endquote
  \renewenvironment{quote}
    { \vspace{3.0\parskip} \oldquote
    \mdframed[backgroundcolor=gray!10]
    \it\small }
    {\endmdframed \endoldquote }
  \mdfsetup{linewidth=0pt,roundcorner=10pt,skipbelow=5pt,skipabove=10pt}
---

## ASSOCIATE EDITOR'S RECOMMENDATION

> Dear Professor Bronstein; Prof Dwyer,
> 
> My recommendation is that manuscript 57722 be declined without prejudice.   The authors use a state of the art computer algorithm known as ``POMDP'' to determine, on the fly, how fisheries should be managed, in terms of the total amount of stock that can be harvested, and the profit accruing from that harvest.   This is an important problem in ecology, and the authors approach appears to offer significant insight.  The reviewers nevertheless point out some important ways in which the text could be improved, and reviewer 1 in particular argues that the authors's approach may be significantly flawed.  These problems would therefore need to be addressed for a revision to be successful.

@@

Reviewer 1's primary objection essentially re-asserts the "paradox of measurement uncertainty" that previous literature has also asserted: that uncertainty should somehow make less cautious.  We appreciate the reviewer highlighting the importance of explaining this central issue properly, and our revisions should make it clear how this erroneous and potentially dangerous conclusion arises from simplifying assumptions.  Reviewer 2's primary objection is the missed opportunity of focusing too narrowly on fisheries.  We agree entirely with the reviewer that the fundamental issues here are germane to ecological management and not specific to fisheries, and have revised the presentation substantially to address this.  Both reviewers raised concerns about the clarity of the methods; so in addition to rewritten discussion of methods we now provide fully executable code to replicate the analysis shown here.  Lastly but most importantly, both reviewers raise the observation that few fisheries are actually managed using a strict constant escapement (CE) policy.  We have introduced more realistic management strategies based on regulating fishing mortality through maximum sustainable yield (MSY) and total allowable catch (TAC), as additional comparisons.  TAC illustrates a different, more heuristic approach to uncertainty than seen in the optimal control methods that provides some valuable additional insights into the challenge of accounting for measurement error. We think this results in a much more interesting manuscript which should be relevant to the broad audience of the American Naturalist.

@@

This is a paradoxical conclusion that defies the precautionary principle, and as such would have important ramifications in ecological management in many applications beyond fisheries.  Further, though the reviewer's analysis is not identical to either the approaches of @Clark1986 or @Sethi2005 (neither assume constant escapement and both find this paradoxical result in only some but not all cases), we believe our analysis provides both a refutation of this result and a clear intuition as to where this misleading conclusion has come from.

@@

Figure 4 offers a clear explanation for when it is optimal to increase harvest in response to increased uncertainty: the POMDP harvest only exceeds the CE harvest when the measured stock size is erroneously low.  That is, when the prior belief would have suggested the observation should be much higher, and therefore the measurement is most likely an error under-estimating the true stock size.  This logic is entirely intuitive and is borne out in the resulting POMDP policies.

@@

The reviewer and editor have raised an important issue in the question of whether we permit the harvest quota to be set to a value higher than the stock.  There are two problems with this.  First, it's not clear how the reviewer implements this assumption in the face of measurement uncertainty: how can one be certain a quota is less than 90% of stock size X without knowing what X is?  One can obviously enforce this with respect to the measured stock size but not the true stock size.  More importantly, this assumption amounts to the assertion that it is mathematically impossible to over-fish a stock to the point of collapse.  However low the stock size might get, local extinction is impossible.  In this world-view, there will always be some tiny fraction of ato-fishes from which the population can recover.  Assuming that local extinction is impossible will indeed bias any optimal decision model to be more aggressive.  Obviously this also has implications for ecological models in general, conservation policy would look different if we assumed extinction was impossible. @Clark1986 already recognized that a very similar assumption in @Reed1979 derivation that stochastic models needed no additional caution ($S=D$) was likely due to the fact that accidentally extinction was impossible (see manuscript, line 150). We do not adopt this assumption.  Obviously real world populations cannot be indefinitely reduced by only a fractional percentage. In our simulations, though we consider a Ricker model, stock abundances are divided into 100 distinct bins, with the smallest bin corresponding to a stock size of zero. Thus it is possible for over-harvesting or stochastic environment, or some combination of both, to lead a population to permanently collapse once it has gotten small enough.

@@

The presentation of all of this material has been entirely re-written in what we hope you will find is a much more appropriate and accessible style.  To avoid needless formalism, we do not rehash the technical details of solving Partially Observed Markov Decision Processes but instead point to the extensive literature already existing on the subject.  Instead, we focus on describing the nature of the problem and how it differs from analyses such as the perfectly observed Markov Decision Process that provides the basis for the Constant Escapement strategy (@Reed1979) and from other Bayesian hierarchical modeling (e.g. partially observed Markov processes, pomp, or Hidden Markov Models, HMMs) which are not decision processes at all, but rather a prerequisite part of choosing & paramaterizing a model, not using said model to make a decision.

> In spite of these negative comments, it seems like the overall approach has a great deal of potential, as Reviewer 2 argues, and if Reviewer 1's concerns prove to be minor, then I believe that a revised version would be a substantial contribution.  That said, the complexity of the technical issues is quite high, and so it may be simpler to submit the manuscript to a journal that specializes in mathematical biology or in fisheries management.
> -- Greg Dwyer

---

# Reviewer #1:

> For complete review, see the attached PDF, which begins as follows:
>
> I attempted to evaluate the papers overall conclusions by a very simple simulation and these results
seem to challenge the papers conclusions.
I simulated a population with the model the authors describe with both observation and process error
lognormally distributed and using the authors parameters. For a range of escapement goals I calculated
the net present value of using that escapement goal, and compared the consequences when there was
no observation error to the case where the lognormal cv was 0.5 – that is very high observation error.
The one difference I made was I did not let the harvest exceed 90% of the total population size ... this
seems reasonable as I know of few fisheries where 90% of the population could be harvested in a single
year.
> 
> The graph below shows a typical result. The thin line is with no observation error, the ticker line with the observation error. In every case the optimal escapement goal was lower when observation error was included.

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.  We believe the differences in our respective results can be explained by the differences in our methods as discussed in our reply to the Editor's discussion of this issue. In short, we believe the reviewer's seemingly counter-intuitive result that increased uncertainty should be met with an action (lowering escapement) that would increase the risk of stock collapse rather then the intuitive response to be cautious by reducing harvest, is simply an artifact of the reviewer's assumption that stock collapse is impossible, and thus increased harvesting poses no real risk.

@@

We agree that the results and methodology could have been much more clearly presented. We hope the rewritten presentation of these results clarifies these issues. In particular, note that once you introduce measurement error a fixed escapement policy can only achieve a fixed *expected* escapement, you never know what the actual escapement is because you never know exactly how many fish you started with.  As measurement errors are equally likely to be too high or too low, a run of "heads", so to speak, would result in consistently over-harvesting and continued decline (see discussion around line 363.)

@@

---

# Reviewer #2:

@@

We thank the reviewer for this careful and constructive review, and agree entirely with the recommendation that the fundamental issues here are not limited to the problem of fishing quotas but are germane to much of ecological decision making. We have now tried both to set up the generic nature of the issue of measurement uncertainty (see Introduction) and discuss its implications beyond fisheries much more explicitly (e.g. lines 423 - 437).  We have however removed the treatment of the tipping point model in order to focus explicitly on the role of uncertainty in the more familiar case of logistic growth, where the dramatic consequences of measurement uncertainty may be less intuitive and cannot be dismissed merely by questioning the frequency of tipping points occurring in real systems.  We hope to address the problem of tipping points more explicitly and more fully in later work.

@@

We now include a formal comparison against TAC-based management policy (and also MSY based policy in the supplement), which reflect this aspect of today's actual management polices which are not updated annually but apply a constant fishing effort (mortality). We also discuss several of the practical objections to implementing POMDP in practice and how it might be modified to address more of these concerns, e.g. lines 456-490.

@@

Excellent observation! Yes, due to the influence of the prior belief, POMDP is slightly more cautious when a stock is rebuilding from small sizes.  We now speak to this in our discussion of Figure 5. We agree with the reviewer's general observation that the POMDP approach allows for more careful tracking of stock size despite measurement error, which in turn leads to both faster rebuilding of stocks and higher economic yields.
